Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-10-08 paper/paper.tex
More replottery

\begin{figure}[tb]
    \centering\includegraphics{gen-graph-non-induced.pdf}
    \caption{Behaviour of algorithms on the non-induced variant. For each plot, the x-axis is the
        pattern edge probability and the y-axis is the target edge probability, both from 0 to 1.
        Along the top row, we show the proportion of instances which are satisfiable; the white
        bands shows the phase transitions, and the black lines are our predictions of where the
        phase transition will occur. On the final three rows, we show the number of search nodes used by the
        Glasgow, LAD and VF2 solvers; the dark regions indicate ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

\begin{figure}[p]
    \centering\includegraphics{gen-graph-induced.pdf}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The fifth row plots constrainedness: the darkest region is where
    $\kappa = 1$, and the lighter regions show where the problem is either over-
    or under-constrained. The final row shows when the Glasgow algorithm performs better when given
    the complements of the pattern and target graphs as inputs---the solid lines show the location
of the phase transition, and the dotted lines are $t_d=0.5$ and the $p_d=t_d$ diagonal.}\label{figure:induced}
\end{figure}

\begin{figure}[tb]
    \centering\includegraphics{gen-graph-sat.pdf}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:non-induced}. The second row shows the number of search nodes used by the
    Glasgow algorithm, the third and fourth rows show the number of decisions made by the pseudo-boolean
and SAT solvers, and the final shows the number of search nodes used on the clique
encoding.}\label{figure:alt}
\end{figure}

>>>>

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[every node/.style={inner sep=0pt, outer sep=0pt}]
        \matrix {
            \node [anchor=center] {}; &
            \node [anchor=center] {\scriptsize $G(10, x){\rightarrowtail}G(150, y)$}; &
            \node [anchor=center] {\scriptsize $G(20, x){\rightarrowtail}G(150, y)$}; &
            \node [anchor=center] {\scriptsize $G(30, x){\rightarrowtail}G(150, y)$}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Satisfiable?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-satisfiable-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-satisfiable-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-satisfiable-30-150.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize Glasgow}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-non-induced-nodes-30-150.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize LAD}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-non-induced-nodes-30-150.pdf}}; &
            \\
            \node [anchor=center] [rotate=90] {\scriptsize VF2}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-non-induced-nodes-30-150.pdf}}; \\
        };
    \end{tikzpicture}

    \caption{Behaviour of algorithms on the non-induced variant. For each plot, the x-axis is the
        pattern edge probability and the y-axis is the target edge probability, both from 0 to 1.
        Along the top row, we show the proportion of instances which are satisfiable; the white
        bands shows the phase transitions, and the black lines are our predictions of where the
        phase transition will occur. On the final three rows, we show the number of search nodes used by the
        Glasgow, LAD and VF2 solvers; the dark regions indicate ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \begin{tikzpicture}[every node/.style={inner sep=0pt, outer sep=0pt}]
        \matrix {
            \node [anchor=center] {}; &
            \node [anchor=center] {\scriptsize $G(10, x)$}; &
            \node [anchor=center] {\scriptsize $G(14, x)$}; &
            \node [anchor=center] {\scriptsize $G(15, x)$}; &
            \node [anchor=center] {\scriptsize $G(16, x)$}; &
            \node [anchor=center] {\scriptsize $G(20, x)$}; &
            \node [anchor=center] {\scriptsize $G(30, x)$}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Satisfiable?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-14-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-15-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-16-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-30-150.pdf}}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Glasgow}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-14-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-15-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-16-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-30-150.pdf}}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize LAD}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-14-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-15-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-16-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-lad-induced-nodes-30-150.pdf}}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize VF2}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-14-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-15-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-16-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-vf2-induced-nodes-30-150.pdf}}; \\
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Constrainedness}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-14-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-15-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-16-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-kappa-30-150.pdf}}; \\
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Complement?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-10-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-14-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-15-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-16-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-20-150.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-which-30-150.pdf}}; \\
        };
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The fifth row plots constrainedness: the darkest region is where
    $\kappa = 1$, and the lighter regions show where the problem is either over-
    or under-constrained. The final row shows when the Glasgow algorithm performs better when given
    the complements of the pattern and target graphs as inputs---the solid lines show the location
of the phase transition, and the dotted lines are $t_d=0.5$ and the $p_d=t_d$ diagonal.}\label{figure:induced}
\end{figure}

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[every node/.style={inner sep=0pt, outer sep=0pt}]
        \matrix {
            \node [anchor=center] {}; &
            \node [anchor=center] {\scriptsize $G(10, x)$}; &
            \node [anchor=center] {\scriptsize $G(12, x)$}; &
            \node [anchor=center] {\scriptsize $G(14, x)$}; &
            \node [anchor=center] {\scriptsize $G(16, x)$}; &
            \node [anchor=center] {\scriptsize $G(18, x)$}; &
            \node [anchor=center] {\scriptsize $G(25, x)$}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Satisfiable?}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-10-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-12-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-14-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-16-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-18-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-satisfiable-25-75.pdf}}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Glasgow}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-10-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-12-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-14-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-16-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-18-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-induced-nodes-25-75.pdf}}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Clasp (PB)}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clasp-induced-nodes-10-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clasp-induced-nodes-12-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clasp-induced-nodes-14-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clasp-induced-nodes-16-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clasp-induced-nodes-18-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clasp-induced-nodes-25-75.pdf}}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Glucose (SAT)}; &
            \node [anchor=center] {\includegraphics*{gen-graph-glucose-induced-nodes-10-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-glucose-induced-nodes-12-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-glucose-induced-nodes-14-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-glucose-induced-nodes-16-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-glucose-induced-nodes-18-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-glucose-induced-nodes-25-75.pdf}}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize BBMC (Clique)}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clique-induced-nodes-10-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clique-induced-nodes-12-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clique-induced-nodes-14-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clique-induced-nodes-16-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clique-induced-nodes-18-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-clique-induced-nodes-25-75.pdf}}; &
            \\
            \node [anchor=center, inner sep=4pt, rotate=90] {\scriptsize Gurobi (MIP)}; &
            \node [anchor=center] {\includegraphics*{gen-graph-gurobi-induced-nodes-10-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-gurobi-induced-nodes-12-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-gurobi-induced-nodes-14-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-gurobi-induced-nodes-16-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-gurobi-induced-nodes-18-75.pdf}}; &
            \node [anchor=center] {\includegraphics*{gen-graph-gurobi-induced-nodes-25-75.pdf}}; &
            \\
        };
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:non-induced}. The second row shows the number of search nodes used by the
    Glasgow algorithm, the third and fourth rows show the number of decisions made by the pseudo-boolean
and SAT solvers, and the final shows the number of search nodes used on the clique
encoding.}\label{figure:alt}
\end{figure}
